|

### 2016-06-03 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
Benchmark

diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
tail(diff_pep,3)

@@

diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
tail(diff_pep,3)

@@

m_table <- merge(x=pnnl, y=dta, by=c("Scan"), all=T)

same <- m_table[(m_table$MSGFDB_SpecEValue.x ==m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]

@@

diff_pep <- m_table[(m_table$Peptide.x != m_table$Peptide.y),]
```

>>>>

diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
print(paste("Different ID:", nrow(diff_pep)))
tail(diff_pep,3)

@@

diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
print(paste("Different ID", nrow(diff_pep)))
tail(diff_pep,3)

@@

m_table <- merge(x=pnnl, y=dta, by=c("Scan"), all=T)
same <- m_table[(m_table$MSGFDB_SpecEValue.x ==m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]

@@

diff_pep <- m_table[(m_table$Peptide.x != m_table$Peptide.y),]
print(paste("Exact same:",nrow(same), "Different Spec eValue:", nrow(diff_spec), "Different Peptides:", nrow(diff_pep)))
print("Different Spec eValue")
#head(diff_spec)

print("Different Peptides")
head(diff_pep)
```

#7. Quantification Benchmark

```{r, echo=F}
setwd("~/Dropbox/_SPACE/Benchmark/11")
q_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_ReporterIons.txt",sep="\t", header = T)
names(q_pnnl)[2] <- "Scan"
q_merge <- merge(frm_docker[,c("Scan","Spec_Evalue", "iTRAQ4.114", "iTRAQ4.115", "iTRAQ4.116", "iTRAQ4.117")], y=q_pnnl[,c("Scan","Ion_114","Ion_115","Ion_116","Ion_117")], by="Scan")

print(paste("No of rows",nrow(q_merge),". Error measured by = |rslt_docker - rslt_pnnl|/rslt_docker"))
err_114 <- abs(q_merge$iTRAQ4.114-q_merge$Ion_114)/q_merge$iTRAQ4.114
print("Ion 114")
summary(err_114)

err_115 <- abs(q_merge$iTRAQ4.115-q_merge$Ion_115)/q_merge$iTRAQ4.115
print("Ion 115")
summary(err_115)

err_116 <- abs(q_merge$iTRAQ4.116-q_merge$Ion_116)/q_merge$iTRAQ4.116
print("Ion 116")
summary(err_116)

err_117 <- abs(q_merge$iTRAQ4.117-q_merge$Ion_117)/q_merge$iTRAQ4.117
print("Ion 117")
summary(err_117)

boxplot(cbind(Ion114=log2(err_114),Ion115=log2(err_115),Ion115=log2(err_116),Ion116=log2(err_117)),main="Log2 relative error")
```
